Concurrent Programming in Harmony

### 2021-01-24 book/paper.tex
Latest

Tuples, lists, strings, and bags are all special cases of dictionaries.
Both tuples and lists map indexes (starting at 0) to Harmony values.
Their format is either \texttt{($e$, $e$, ..., $e$,)} or
\texttt{[$e$, $e$, ..., $e$,]}.
If the tuple or list has two or more elements, then the final comma
is optional.
A string is represented as a tuple of its characters.
Characters are one-character atoms, which can be expressed
in hexadecimal unicode using the syntax \texttt{.0xXX}.
A bag or multiset is a dictionary that maps a value to how many
times it occurs in the bag.
The syntax is \texttt{bag\{ $e$, $e$, ... \}}.

@@

@@

Harmony has native support for bags (aka multisets), which are sets
that can contain multiple copies of the same element.
It is represented by a dictionary that maps each element to its
multiplicity.
So \texttt{bag\{ 10, 10, 12 \} = dict\{ 10:2, 12:1 \}}.

The \texttt{bag} module (\autoref{ap:bag}) contains various
convenient routines that operate on lists or tuples.
Native operations on bags include the following:

@@

Bags also support comprehension.

>>>>

Tuples, lists, strings, and bags are all special cases of dictionaries.
Both tuples and lists map indexes (starting at 0) to Harmony values.
Their format is either \texttt{($e$, $e$, ..., $e$,)} or
\texttt{[$e$, $e$, ..., $e$,]}.
If the tuple or list has two or more elements, then the final comma
is optional.
A string is represented as a tuple of its characters.
Characters are one-character atoms, which can be expressed
in hexadecimal unicode using the syntax \texttt{.0xXX}.
A bag or multiset is a dictionary that maps a value to how many
times it occurs in the bag.

@@

Native operations on strings include the following:

\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{$s~k$} & indexing \\
\hline
\texttt{$s$ + $s$ + ...} & concatenation \\
\hline
\texttt{$s$ * $n$} & $n$ copies of $s$ concatenated \\
\hline
\texttt{$c$ [not] in $s$} & check if $c$ (a one-character atom) is in $s$ \\
\hline
\texttt{len $s$} & the length of $s$ \\
\hline
\end{tabular}
\end{center}

@@

A bag is represented by a dictionary that maps each element to its
multiplicity, for example: \{ 10:2, 12:1 \}.
The \texttt{bag} module (\autoref{ap:bag}) contains various
convenient routines that operate on lists or tuples.
Native operations on bags include the following:

@@
